---
title: "A3_Tianyi_Zuo"
author: "Tianyi Zuo"
date: "2022/1/26"
output: html_document
---

### GitHub username: Lydia12138
### Date: 2022-01-26 Repo:https://github.com/Lydia12138/Assignment-3-

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)#package loading
```

```{r}
MyData<-read.csv("./InputData/FallopiaData.csv")#loading the data
str(MyData)#check the structure of the Data
head(MyData)
class(MyData)
dim(MyData)
tail(MyData)
summary(MyData)
```


## Remove rows with 'Total' biomass < 60
```{r}
MyData <- MyData %>%
  filter(Total >= 60)
```

## Reorder the columns so that they are in the order: ‘Total’, ‘Taxon’, ‘Scenario’, ‘Nutrients’, and remove the other columns
```{r}
SubData <- select(MyData, Total, Taxon, Scenario, Nutrients)
head(SubData)
```

## Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG, and add it to the dataset.
We know that converts the 1 mg equal to 0.001 grams. Here I add a new column TotalG with different units(grams), and TotalG is Total divide 1000.
```{r}
NewData <- transmute(SubData,TotalG = Total / 1000, Taxon, Scenario, Nutrients)
head(NewData)
```

## Write a custom function that will take two inputs from the user: 
1. a vector of data to process (e.g. column from a data.frame object) and 
2. a string that defines what calculation to perform.
if string #2 is "Average" then calculate the average value for the column named in vector #1
if string #2 is "Sum" then calculate the sum of values for the column named in vector #1
if string #2 is "Observations" then count the number of observed values for the column named in vector #1
if string #2 is anything else, then output an error to the user 

```{r}
# Write a custom function have two inputs from the user: vec1 is a vector, and str1 is a string.
# used else if to achieve the function
my_function <- function(vec1, str1){
  if (str1 == "Average"){
    Average <- mean(vec1)
    return(Average)
  }else if (str1 == "Sum"){
    Sum <- sum(vec1)
    return(Sum)
  }else if (str1 == "Observation"){
    Count <- length(vec1)
    return (Count)
  }else {
    cat("Error! You can choose from Average/Sum/Observation.")
  }
}
```

## Uses the function to count the total number of observations in the 'Taxon' column
```{r}
cat("The total number of observations is", my_function(NewData$Taxon,"Observation"))
```

## Uses the function  to calculate the average TotalG for each of the two Nutrient concentrations
```{r}
NewData %>% group_by(Nutrients) %>% 
  summarise(Average_TotalG = my_function(TotalG, "Average"))
```


## Write (i.e. save) the new data to a file called "WrangledData.csv" in the Output folder.
```{r}
write.csv(NewData, "Output/WrangledData.csv", row.names = FALSE)
```


## Test the function
```{r}
Vector <- c(1,2,3,4,5,6,7,8,9,10)
# here I used this vector to test my function.  The output should be average = 5.5, sum = 55, Observation = 10 for this vector
my_function(Vector, "Average")
```
```{r}
my_function(Vector, "Sum")
```
```{r}
my_function(Vector, "Observation")
```


